Article template&#58; A reproducible RMarkdown template for Elsevier's journal format with examples for beginners

### 2019-02-12 Paper/Manuscript.Rmd
Add a basic table + fix variable name

``` {r libraries, echo=FALSE, cache=FALSE, results="hide", message=FALSE, warning = FALSE}
## code chunk for libraries that are required to be installed + loaded for this template
# note the first word after `{r...` in the chunk header above is the name of this chunk. 
# Names must be unique and not have spaces (underscores are ok), so name with CamelCaseLikeThis or snake_case_like_this
require(tidyverse)
#require(ggExtra)
#require(gridExtra)
require(here)
require(knitr)
require(stargazer)
#require(RColorBrewer)
#require(ggrepel)
#require(ggpmisc)
```

@@

# characterize petal length into 5 categories in increments of 1.5 cm
df  = df%>%
  mutate(petel_length_level = ifelse(petal_length>= 6 & petal_length <7.5,"VeryHigh",0))%>%   
  mutate(petel_length_level = ifelse(petal_length>= 4.5 & petal_length <6,"High",petel_length_level))%>%  
  mutate(petel_length_level = ifelse(petal_length>= 3 & petal_length <4.5,"Medium",petel_length_level))%>%
  mutate(petel_length_level = ifelse(petal_length>= 1.5 & petal_length <3,"Low",petel_length_level))%>%
  mutate(petel_length_level = ifelse(petal_length <1.5,"VeryLow",petel_length_level))

# order new petal length categories correctly from Low to High
df = df%>%mutate(petel_length_level = as.factor(petel_length_level))
df$petel_length_level = factor(df$petel_length_level, levels=c("VeryLow","Low","Medium","High","VeryHigh"))
```

@@

-   Add your 3 -5 highlights
-   As bullets here
-   Making sure each is less than 85 characters in length

@@

# Examples
# Heading level 1
## Heading level 2
### Heading level 3
Here's how to **bold** or *italic* a piece of text.

@@

>>>>

``` {r libraries, echo=FALSE, cache=FALSE, results="hide", message=FALSE, warning = FALSE}
## code chunk for libraries that are required to be installed + loaded for this template
# note the first word after `{r...` in the chunk header above is the name of this chunk. 
# Names must be unique and not have spaces (underscores are ok), so name with CamelCaseLikeThis or snake_case_like_this
require(tidyverse)
#require(ggExtra)
#require(gridExtra)
require(here)
require(knitr)
require(stargazer)
#require(RColorBrewer)
#require(ggrepel)
#require(ggpmisc)
require(gt)
```

@@

# characterize petal length into 5 categories in increments of 1.5 cm
df  = df%>%
  mutate(petal_length_level = ifelse(petal_length>= 6 & petal_length <7.5,"VeryHigh",0))%>%   
  mutate(petal_length_level = ifelse(petal_length>= 4.5 & petal_length <6,"High",petal_length_level))%>%  
  mutate(petal_length_level = ifelse(petal_length>= 3 & petal_length <4.5,"Medium",petal_length_level))%>%
  mutate(petal_length_level = ifelse(petal_length>= 1.5 & petal_length <3,"Low",petal_length_level))%>%
  mutate(petal_length_level = ifelse(petal_length <1.5,"VeryLow",petal_length_level))

# order new petal length categories correctly from Low to High
df = df%>%mutate(petal_length_level = as.factor(petal_length_level))
df$petal_length_level = factor(df$petal_length_level, levels=c("VeryLow","Low","Medium","High","VeryHigh"))
```

@@

-   Add your 3 -5 highlights
-   As bulletpoints here
-   Making sure each is less than 85 characters in length

@@

## Markdown
Here are some examples of how to format text with Markdown.

# Heading level 1
## Heading level 2
### Heading level 3

Here's how to **bold** or *italicize* a piece of text.

@@

## Tables
Here is an example of a table created from the .csv file in the `SupplementaryMaterial/Data`folder using the `gt` package from RStudio. You can read more about `gt` [here](https://github.com/rstudio/gt), and there's helpful examples to further customize tables (eg with color, foototes, significant figures, re-labeling columns, and more) [here](https://github.com/allisonhorst/gt-awesome-tables).

```{r}
df %>% 
    sample_n(5) %>%   # select 5 random rows from the dataframe
    select(iris_class, sepal_length, petal_length, petal_length_level) %>%  # show only these columns (in this order)
    gt () %>% #make a table
    tab_header( 
    title = "Example irises", # ...with this title
    subtitle = "Data on five randomly selected irises")

```
